### 2025-07-29 docs/article/Sections/results.tex
section 6 improvements

However, our results diverge from theirs regarding memory usage. 
They reported lower heap usage for Java virtual threads (16–64~MB) compared to 
Kotlin coroutines (52–99~MB), which contrasts with our measurements. 
This discrepancy may be attributed to the different workloads: while their 
benchmark includes a single I/O read-write operation per request, our experiments 
focus exclusively on read-only I/O tasks.

@@

Our observations suggest that the choice between Virtual Threads and
suspendable coroutines should be guided by both runtime behavior and
development preferences. Virtual Threads offer the simplicity of synchronous
programming with competitive performance in moderate-load scenarios. In
contrast, suspendable coroutines, while requiring an asynchronous programming
model, may offer better efficiency in applications with higher concurrency,
deeper stacks, or more dynamic workloads.

>>>>

Our results diverge from theirs regarding memory usage. They reported lower
heap usage for Java virtual threads (16–64~MB) compared to Kotlin coroutines
(52–99~MB), which contrasts with our measurements. This discrepancy may be
attributed to the different workloads: while their benchmark includes a single
I/O read-write operation per request, our experiments focus exclusively on
read-only I/O tasks.

@@

Our observations suggest that the choice between Virtual Threads and
suspendable coroutines should be guided by both runtime behavior and
development constraints. Virtual Threads offer the compelling advantage of
preserving synchronous programming semantics while achieving competitive
performance across moderate to high-load scenarios—a significant benefit for
teams migrating existing codebases or working with legacy template engines.
Suspendable coroutines, while requiring developers to adopt asynchronous
programming paradigms, may provide greater efficiency in scenarios involving
high concurrency, deeper call stacks, or highly dynamic workloads.

The framework-specific variations observed in our results—particularly the
performance differences between Spring WebFlux and Quarkus
implementations—suggest that the underlying reactive runtime architecture
significantly influences the effectiveness of each approach. This finding
underscores the importance of considering not only the concurrency model but
also the specific framework ecosystem when making architectural decisions for
PSSR implementations.
